TacticToe: Learning the Game of Tactics

### 2018-02-05 tactictoe_jv.tex
updating todo
Minor tweak in abstract

We bridge this gap by implementing our tactical prover TacticToe on top 
of the HOL4 ITP. 
TacticToe first learns from many proof scripts
the relevance of tactics in particular proof situations.
This learned knowledge is then used in a Monte Carlo tree search algorithm that explores the most promising tactic-level proof paths. 
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.2\% 
of 7164 theorems of the standard library where as 
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the 
result of both provers.
\end{abstract}

@@

>>>>

We bridge this gap by implementing our tactical prover TacticToe on top
of the HOL4 ITP.
TacticToe first learns from many proof scripts
the relevance of tactics in particular proof situations.
This learned knowledge is then used in a Monte Carlo tree search algorithm that explores the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.2\%
of the 7164 theorems in HOL4's standard library whereas
Eprover solves 34.5\%. The success rate rises to 69.0\% by combining the
results of both provers.
\end{abstract}

@@

mention proof obligations (use this word) return by a tactic.
